Wavelet Vignette

### 2015-06-23 talks/twentymin_seminar.Rmd
update

% False Discovery Rates, A New Deal
% Matthew Stephens
% 2014/5/8

```{r, include=FALSE}
require("qvalue")
require("ashr")
require("ggplot2")
```

```{r setup, include=FALSE}
# set global chunk options
opts_chunk$set(cache=TRUE,autodep=TRUE,warning=FALSE,dev='pdf')
dep_auto()
```

# What you can expect from this talk

- No experimental data!

- No fancy heatmaps!

- 100\% Money-back guarantee to half the False Discovery Rate (FDR) in your data!

# The Canonical Genomics Experiment

@@

- Apply `qvalue` 
to identify findings ``significant" at a given FDR.

- ...?

@@

# Problem 1: The Zero Assumption (ZA)

@@

# Problems: Summary

Standard tools are highly conservative.

@@

# FDR via Empirical Bayes

@@

@@

- *Incorporate precision* of each observation $\hat\beta$ into the likelihood.
Specifically, approximate likelihood for $\beta_j$ by assuming 
$$\hat\beta_j \sim N(\beta_j, s_j)$$

# FDR - A New Deal

@@

# Recall Problem 1: distribution of alternative Z values multimodal
```{r, echo=FALSE,fig.height=4,fig.cap=""}
nullalthist(hh.zscore,hh.fdrtool$lfdr,main="qvalue")  
```

# Problem Fixed: distribution of alternative Z values unimodal
```{r, echo=FALSE,fig.height=4,fig.cap=""}
nullalthist(hh.zscore,hh.ash$lfdr,main="ash")
```

# Example: FDR estimation

```{r, echo=FALSE,fig.height=4,fig.cap=""}
  plot_FDReg_hist(hh.pval,hh.q$pi0,type=4,title="qvalue")                 
```

# Example: FDR estimation

```{r, echo=FALSE,fig.height=4,fig.cap=""}
  plot_FDReg_hist(hh.pval,get_pi0(hh.ash),type=4,title="ash")                 
```

@@

# Recall Problem 2: poor measurements dilute good measurments

@@

# A new problem: an embarrassment of riches

- If the null is mostly false, the new approach can  provide unsettling results

@@

# Perhaps we didn't really understand the question?

- Problem arises only if we insist on asking question ``is $\beta_j=0$?"

@@

- Suggests a change of focus: assume *none* of the $\beta_j$ are zero ("one group approach"), and ask for which $\beta_j$ are we confident about the sign (Gelman et al, 2012).

# The False Sign Rate

- Suggestion: replace FDR with local false sign rate (lfsr), the probability that if we say an effect is positive (negative), it is not.

- Example: suppose we estimate that $\Pr(\beta_j<0)=0.975$ and $\Pr(\beta_j>0)=0.025$. Then we report $\beta_j$ as a ``(negative) discovery", and estimate its fsr as 0.025.

# Even with many signals, large $p$ values have high lfsr

```{r, echo=FALSE,fig.height=4,fig.cap="",warning=FALSE,message=FALSE}
  res=data.frame(p=hh.pval, lfsr=hh.ash$lfsr, qvalue = hh.ash$qvalue)
  res.melt = melt(res, id.vars=c("p"),variable.name="Measure")
cbbPalette <- c("#000000", "#D55E00", "#CC79A7")
 labels = c('qvalue','lfsr')
  breaks = c("qvalue","lfsr")

  pp= ggplot(data=res.melt,aes(p,value,color=Measure)) +geom_point(shape=1) +
      geom_abline(colour = "black") +
        xlab("p-value") +
        ylab("lfsr/qvalue")

  print(pp +scale_y_continuous(limits=c(0,0.1)) +
          scale_x_continuous(limits=c(0,0.1))  +
           scale_colour_manual(values=cbbPalette,breaks=breaks,labels=labels) +
          coord_equal(ratio=1))

```

# Summary

- ASH provides a generic approach to shrinkage estimation, as well as
false discovery (sign) rates.

- Unimodal assumption for effects reduces conservatism

- But by using two numbers ($\hat\beta,s$) instead of one ($p$ values or $z$ scores) precision of different measurement is better accounted for.

- In high-signal contexts, False Sign Rate is preferable to False Discovery Rate.

# Reproducible Research?

- Principle: when publishing results of computational procedures, we should
publish the code that produced the results.
- "publishing figures or results without the complete software environment could
be compared to a mathematician publishing an announcement of a mathematical theorem without giving the proof" (Buckheit and Donohoe)
- “an article about a computational result is advertising, not scholarship. The actual scholarship is the full software environment, code and data, that produced the result.” [Claerbout]

# This talk is reproducible!

- `http://www.github.com/stephens999/ash`

# Why is reproducibility important?

- Not only because people are forgetful, error-prone, or dishonest!
- Reproducing work is also the first step to extending it.
- Helps communications among researchers (eg student + advisor).

# Thanks

- to the developers of **R**, **knitr**, **Rstudio** and **Pandoc**.

@@

- Including Ester Pantaleo, Scott Powers, Mengyin Lu, Sen Tian, Wei Wang, Zhengrong Xing.

- NHGRI for funding.

- `ashr` package: `http://www.github.com/stephens999/ash`

# Pandoc Command used

`pandoc -s -S -i --template=my.beamer -t beamer -V theme:CambridgeUS -V colortheme:beaver  slides.md -o slides.pdf`

(alternative to produce html slides; but figures would need reworking)
`pandoc -s -S -i -t dzslides --mathjax slides.md -o slides.html`

Here is my session info:

```{r session-info}
print(sessionInfo(), locale=FALSE)
```

# Issue: you can't actually estimate $\pi_0$!

- Data cannot distinguish between $\beta_j = 0$ and $\beta_j$ "very
small"

- As a result $\pi_0$ cannot be estimated: the data can never rule out $\pi_0=0$.

- But the unimodal constraint bounds how big $\pi_0$ can be.

- Use penalized likelihood to make $\pi_0$ ``as big as possible",
subject to the unimodal constraint.

# Approach remains conservative (if unimodal assumption holds)

```{r,echo=FALSE,include=FALSE}
load("../paper/Rcode/sim1.RData") #load simulation results
source("../paper/Rcode/plot_pi0.R")
```

```{r, echo=FALSE,fig.height=4,fig.cap=""}
plot_pi0_onlyqval(list(simres1a,simres2))
```

# Next steps?

- Incorporate $t$ likelihood as well as normal.

- Incorporate shrinkage of variances and not just means.

- Extend to allow $g(\cdot;\pi)$ to depend on covariates $X$.

- Extend to allow for correlations in the measured $\hat\beta_j$.

# Is this an important problem?

- The original paper introducing FDR (Benjamini and Hochberg, 1995) has
been cited 21,787 times according to Google Scholar.

- That is three times a day for the last 19 years!

# FDR and q values

Although precise definitions vary, roughly

- The FDR at a threshold $P$ is 
$$\text{FDR}(P)=\Pr(\beta_j = 0 |  p_j<P).$$

- The q value for observation $j$ is $q_j=\text{FDR}(p_j)$.

# Estimation and Shrinkage

- Besides allowing one to estimate fdr and fsr, 
this approach also provides a posterior distribution for each $\beta_j$.

- So for example we can easily compute fdrs for discoveries other than ``non-zero" (eg compute $\Pr(\beta_j > 2 | \hat\beta_j)$).

- And use it to obtain point estimates and credible intervals for each $\beta_j$, taking account of information from all the other $\beta_j$.

- Because $f(\beta)$ is unimodal, the point estimates will tend to be ``shrunk" towards the overall mean (0).

- Because $f(\beta)$ is estimated from the data, the amount
of shrinkage is adaptive to the data. And because of the role of $s_j$, the amount of shrinkage adapts to the information on each gene.

>>>>

---
title: "False Discovery Rates, A New Deal"
author: Matthew Stephens
date: June 12, 2015
output: ioslides_presentation
---

```{r, include=FALSE}
require("qvalue")
require("ashr")
require("ggplot2")
require("knitr")
```

```{r setup, include=FALSE}
  #set global chunk options
  opts_chunk$set(cache=FALSE,autodep=TRUE,warning=FALSE)
  dep_auto()
```

## How can we make more progress together?

- Abstract our problems
- Develop benchmarks
- Build generic tools

## The power of generic tools

- Linear regression
- k-means clustering
- Principal Components Analysis
- qvalue for FDR

Goal: generic tools for shrinkage estimation

## The Canonical Genomics Experiment

@@

- Apply `qvalue` 
to estimate FDR at any given threshold.

$$\text{FDR}(\gamma)=\Pr(\beta_j = 0 |  p_j< \gamma).$$

- ...

@@

## The outsize impact of generic procedures

- The original paper introducing FDR (Benjamini and Hochberg, 1995) has
been cited 27,331 times (June 2015) according to Google Scholar.

- That is three times a day for the last 20 years!

- More than ten times a day for the last year!

## Problem 1: The Zero Assumption (ZA)

@@

## Problems: Summary

@@

(Both tend to lead to conservative behaviour: overestimating FDR)

## Can we do better?

Two Ideas:

- Use two numbers ($\hat\beta_j,s_j$) instead of one number ($p_j$ or $z_j$).

- Introduce "modelling assumption": distribution of $\beta_j$ is unimodal about 0.

## FDR via Empirical Bayes

@@

- Various semi-parametric approaches taken to estimating $f_1$. For example,
Efron uses Poisson regression; Muralidharan uses mixture of normal distributions.

@@

- *Incorporate precision* of each observation $\hat\beta$ into the likelihood:
$$\hat\beta_j | s_j \sim N(\beta_j, s_j)$$

(cf Bayes inference from summary statistics; V.Johnson, J.Wakefield)

## FDR - A New Deal

@@

## Adaptive Shrinkage

- This approach actually provides a full posterior distribution for each $\beta_j$.

- So easy to obtain point estimates and credible intervals.

- Because $g(\beta)$ is unimodal, the point estimates (and CIs) will tend to be ``shrunk" towards the overall mean (0).

- Because $g(\beta)$ is estimated from the data, the amount
of shrinkage is adaptive to signal in the data. And because of the role of $s_j$, the amount of shrinkage adapts to the information on each observation.

## Recall Problem 1: distribution of alternative Z values multimodal
```{r, echo=FALSE,fig.height=4,fig.cap=""}
nullalthist(hh.zscore,hh.fdrtool$lfdr,main="qvalue")  
```

## Problem Fixed: distribution of alternative Z values unimodal
```{r, echo=FALSE,fig.height=4,fig.cap=""}
nullalthist(hh.zscore,hh.ash$lfdr,main="ash")
```

## Recall Problem 2: poor measurements dilute good measurments

@@

@@

## Some more extensive simulations

![Image](../paper/figures/scenarios_density.pdf)

$$\beta_j \sim \pi_0 \delta_0(.) + (1-\pi_0) g(.)$$

Goals: Estimate $\pi_0$? Estimate $g$?

## Estimation of $\pi_0$

![Image](../paper/figures/pi0_est.pdf)

All methods are, generally, "conservative" (deliberately).

## Estimation of $g$

- Estimating $g$ is a “deconvolution problem”.
- Notoriously difficult in general. 
- Efron emphasises the difficulties of implementing a stable general algorithm:

<div class="red">
“the effort foundered on practical difficulties involving the perils of deconvolution... Maybe I am trying to be overly nonparametric... but it is hard to imagine a generally satisfactory parametric formulation...”
</div>

## Unimodal assumption stabilizes estimation of $g$

![Image](../paper/figures/egcdf.pdf)

## A new problem: an embarrassment of riches

- If the null is mostly false, this approach can  provide unsettling results

@@

## Perhaps we didn't really understand the question?

- Problem arises only if we insist on asking question "is $\beta_j=0$?"

@@

- Suggests a change of focus: ask for which $\beta_j$ are we confident about the sign (cf Gelman et al, 2012; Tukey 1961).

## Generic procedure: summary

- Inputs: $(\hat{\beta}_1,s_1), \dots, (\hat{\beta}_p,s_p)$
- Assumptions:

$$\hat{\beta}_j | \beta_j, s_j \sim N(\beta_j,s_j)$$
$$\beta_j | s_j \sim g(), \text{unimodal}.$$

- Output: estimate of $g$; "shrunken" posterior distribution for $\beta_j$.

## Generic procedure: embellishments

- Inputs: $(\hat{\beta}_1,s_1), \dots, (\hat{\beta}_p,s_p)$
- Assumptions:

$$\hat{\beta}_j | \beta_j, s_j \sim t(\beta_j,s_j)$$
$$\beta_j | s_j \sim s_j^\alpha g(), \text{unimodal}.$$

- Output: estimate of $g$; "shrunken" posterior distribution for $\beta_j$.

## Other Applications

- Widely applicable: requiring only an estimated
effect size and standard error for each object.

- E.g. Currently applying it to wavelet shrinkage applications.

## Next steps?

- Incorporate shrinkage of variances and not just means. (e.g. ``moderated $t$ test", Smyth et al).

- Allow $g(\cdot;\pi)$ to depend on covariates $X$.

- Allow for correlations in the measured $\hat\beta_j$.

- Multivariate version: we observe a matrix of $\hat\beta_j$ and $s_j$ values.

## Thanks

- to the developers of **R**, **knitr**, **Rstudio** and **Pandoc**.
Also the very cool **SQUAREM** package.

@@

- Including  Chaoxing Dai, Mengyin Lu, Ester Pantaleo, Scott Powers, Sen Tian, Wei Wang, Zhengrong Xing.

- NHGRI, Moore Foundation for funding.

- `ashr` package: `http://www.github.com/stephens999/ashr`

### 2015-06-23 talks/wavelet_vignette.rmd
update

---
title: "Dynamic Statistical Comparisons, and other adventures in getting organized"
author: Matthew Stephens
date: May 22, 2015
output: ioslides_presentation
---

```{r, include=FALSE}
require("qvalue")
require("ashr")
require("ggplot2")
require("knitr")
```

```{r setup, include=FALSE}
  #set global chunk options
  opts_chunk$set(cache=TRUE,autodep=TRUE,warning=FALSE)
  dep_auto()
```

## Getting Organized!

- Over ~10 years of working with graduate students + postdocs,
I've noticed something.
- Organized researchers get more done (and better!).
- Many of them are more organized than I am.
- Thought: I should get organized; I should help others get organized.

## So what can you do?

- Buy a notebook; bring it to meetings; make notes! 
- Come to meetings with a written agenda. 
- While doing research, record what you did and what the outcome was.
- Use version control ([git](http://git-scm.com)) and internet repositories ([bitbucket](http://www.bitbucket.org), [github](http://www.github.com)) to organize notes, code, etc.
- Use *knitr* to help make your research reproducible.
- Talk about the tools you find useful!

## What are these repository things?

- A repository: a central place in which an aggregation of data is kept and maintained in an organized way (searcharticle.com)
- Great for sharing material across multiple people (eg student and advisor!)
- An amateur example: [http://github.com/stephens999/ash](http://github.com/stephens999/ash)

## What is knitr?

- An R package
- A tool for literate programming
- Text, and R code are interleaved
- When you compile the document, the code is run, and output inserted into the text.
- Great for writing reports, and keeping a track of what you did and what the result was!
- This talk was written with knitr (with RStudio)!

## What is knitr?

 ![Image](screenshot.png)

## What is Reproducible Research?

- Principle: when publishing results of computational procedures, we should
publish the code that produced the results.
- "publishing figures or results without the complete software environment could
be compared to a mathematician publishing an announcement of a mathematical theorem without giving the proof" (Buckheit and Donohoe)
- “an article about a computational result is advertising, not scholarship. The actual scholarship is the full software environment, code and data, that produced the result.” [Claerbout]

## Why is reproducibility important?

- Not only because people are forgetful, error-prone, or dishonest!
- Reproducing work is also the first step to extending it.
- Helps communications among researchers (eg student + advisor).
- If you do not publish code implementing your methods, your methods will likely go unused.

## More on git, github, knitr, reproducibility

- Google "The git book", to get started on git.
- Google "Karl Broman github tutorial" for statistics-oriented intro to github.
- Google "donohoe buckheit" for "Wavelab and reproducible research"

## More ridiculously-personal tips

- "Don't try to show them how clever you are" (BD Ripley)
- Minimise email for research communications 
- Chunk time
- Relax! (Exercise, Vacation)
- Admin on Fridays
- Learn some programming principles
- Benchmark early and often

## Minimise email

![Image](slack.screenshot.png)

## Benchmarking:

By which I mean, any quantitative assessment and comparisons of performance (accuracy; speed).

## Benchmarking:

Benefits include:

- Communication
- Tweaking/honing
- Basic quality assurance (cf "testing")

## Benchmarking:

Even basic benchmarks have benefits (...Done is better than perfect)

## Dynamic Statistical Comparisons

- Overall Goal: Improve how we, in the statistics community, make comparisons among methods.

- Reduce work and redundancy; make comparisons more transparent

- How? Centralize reproducible statistical comparisons in easily-extensible public repositories.

## Inspiration: Public Benchmarking

- Protein folding (CASP)

- Image analysis (Pascal)

- The Neflix Prize

- Genetics Analysis Workshop

- RECOMB/DREAM challenge

- Sage Bionetworks

## Dynamic Statistical Comparisons: advantages

- Authors can run their own methods. 
- Ease of adding new data can quickly uncover over-tuning to specific datasets.
- Work is divided, and not duplicated.
- Promotes collaboration through competition. 
- Ensures results are reproducible, and extendable.

- [http://stephens999.github.io/blog/](http://stephens999.github.io/blog/) for more on DSC

## DSC Requirements

- Well-defined input format for methods
- Well-defined output format
- Scoring function (output, input, meta-data)
- Ways to produce input, meta-data
- Methods to turn input -> output

## DSCR - an R package

- Define Scenarios (produce input, meta-data)
- Define Methods (turn input -> output)
- Define Scores

A simple function call then runs all methods on all scenarios, outputs scores

[Simple Vignette](http://htmlpreview.github.com/?https://github.com/stephens999/dscr/blob/master/vignettes/one_sample_location.html)

## DSC examples we're working on

- Covariance Estimation
- Large-scale linear regression
- 1-D Smoothing with Wavelets [after Antoniadis et al, 2001]

## Wavelet Smoothing Example: The "Blocks" Function

@@

## Wavelet Shrinkage

- WCs of true mean ($$\beta$$) are "sparse" (or at least, have spiky density about 0)

- WCs for observed data ($$\betahat$$) are noisy observations of true WCs.

- If we shrink the $$\betahat$$ toward 0, they will give a better estimate for $$\beta$$

- And inverting the wavelet transform will give better estimate for $\mu$

## Shrink + Backtransform = Smooth

```{r, echo=FALSE}
y.wd.thresh = wavethresh::threshold(y.wd, policy="BayesThresh")
y.est = wavethresh::wr(y.wd.thresh)
plot(x,mu,type="l",col=2,lwd=2)
lines(x,y.est,type="l")
```

## How to Shrink?

We've been developing generic EB approaches to shrinkage estimation:

- Assume $\beta_j \sim g()$ where $g$ has some concentration about 0 ("sparse").

- Assume we have corresponding estimates $\hat\beta_j$, with standard error $s_j$.

- 
## How to Shrink?

- *Incorporate precision* of each observation $\hat\beta$ by assuming
$$\hat\beta_j | \beta_j \sim N(\beta_j, s_j^2)$$

- Constrain $g$ to be *unimodal* about 0;

- Shrink via two-stage procedure: first estimate $g$ "non-parametrically" from data; then
compute $p(\beta_j | \hat{g}, \hat\beta_j,s_j)$.

## Details

- A convenient way to model $g$: mixture of 0-centered
normal distributions: 
$$g(\beta; \pi) = \sum_{k=1}^K \pi_k N(\beta; 0, \sigma^2_k)$$

- Estimating $g$ comes down to estimating $\pi$. Joint estimation of $\pi_0,\pi$ easy by maximum likelihood (EM algorithm).

- By allowing $K$ large, and $\sigma_k$ to span a dense grid of values,
we get a flexible unimodal symmetric distribution.

- Can approximate, arbitrarily closely, any scale mixture of normals.
Includes almost all priors used for sparse regression problems (spike-and-slab, double exponential/Laplace/Bayesian Lasso, horseshoe).

## Illustration: $g$ a mixture of 0-centered normals

```{r, echo=FALSE,fig.height=4,fig.cap=""}
x=seq(-4,4,length=100)
plot(x, dnorm(x,0,1),type="l",ylim=c(0,2),ylab="density")
lines(x, dnorm(x,0,0.1))
lines(x, dnorm(x,0,0.5))
```

## Illustration: $g$ a mixture of 0-centered normals

```{r, echo=FALSE,fig.height=4,fig.cap=""}
x=seq(-4,4,length=100)
plot(x, 0.5*dnorm(x,0,1)+0.5*dnorm(x,0,0.1),type="l",ylim=c(0,2),ylab="density")
```

## Illustration: $g$ a mixture of 0-anchored uniforms

```{r, echo=FALSE,fig.height=4,fig.cap=""}
x=seq(-4,4,length=100)
plot(x, dunif(x,0,1),type="s",ylim=c(0,5),ylab="density")
lines(x, dunif(x,0,0.2),type="s")
lines(x, dunif(x,0,0.5),type="s")
lines(x, dunif(x,-0.3,0),type="s",col=2)
lines(x, dunif(x,-0.4,0),type="s",col=2)
lines(x, dunif(x,-2,0),type="s",col=2)
```

## Illustration: $g$ a mixture of 0-anchored uniforms

```{r, echo=FALSE,fig.height=4,fig.cap=""}
x=seq(-4,4,length=100)
plot(x, 0.1*dunif(x,0,3)+ 0.3*dunif(x,0,0.2) + 0.2*dunif(x,0,0.5) + 0.1* dunif(x,-0.3,0) + 0.1*dunif(x,-0.3,0)+0.2*dunif(x,-0.4,0),type="s",ylim=c(0,2),ylab="density")
```

## Adaptive Shrinkage

- Approach provides posterior distribution for each $\beta_j$.

- For wavelet shrinkage we just use posterior mean.

- Because $g(\beta)$ is unimodal, the point estimates (and CIs) will tend to be "shrunk" towards the overall mean (0).

- Because $g(\beta)$ is estimated from the data, the amount
of shrinkage is adaptive to signal in the data. And because of the role of $s_j$, the amount of shrinkage adapts to the information on each observation.

- So we call the approach "Adaptive Shrinkage" (ash).

## Smoothing with Adaptive Shrinkage (smash)

```{r, echo=FALSE, results='hide', message=FALSE}
load("../../dscr-smash/res.RData")
library("dplyr")
library("ggplot2")
res.1.v1 = res %>% filter(grepl(".1.v1",scenario)) %>% filter(method %in% c("smash.haar","smash.homo.s8","ebayesthresh","sure.homo.s8"))
PLOTNAMES=c("angles","blip","blocks","bump","corner","doppler","spike")
res.1.v1$scenario=factor(res.1.v1$scenario,levels=paste0(c("ang","blip","blk","bump","cor","dop","sp"),".1.v1"))
levels(res.1.v1$scenario)=PLOTNAMES
ggplot(res.1.v1,aes(x=method,y=mise,fill=method)) + geom_violin() + facet_grid(.~scenario) + theme(axis.text.x=element_blank())
```

## Homoskedastic errors

```{r, echo=FALSE, results='hide', message=FALSE}
res.1.v1 = res %>% filter(grepl(".1.v1",scenario)) %>% filter(method %in% c("smash.haar","smash.homo.s8","ebayesthresh"))

PLOTNAMES=c("angles","blip","blocks","bump","corner","doppler","spike")
res.1.v1$scenario=factor(res.1.v1$scenario,levels=paste0(c("ang","blip","blk","bump","cor","dop","sp"),".1.v1"))
levels(res.1.v1$scenario)=PLOTNAMES

ggplot(res.1.v1,aes(x=method,y=mise,fill=method)) + geom_violin() + facet_grid(.~scenario) +theme(axis.text.x=element_blank())
```

## Heteroskedastic errors

```{r, echo=FALSE, results='hide', message=FALSE}
res.1.v4 = res %>% filter(grepl(".1.v4",scenario)) %>% filter(method %in% c("smash.haar","smash.homo.s8","ebayesthresh"))
res.1.v4$scenario=factor(res.1.v4$scenario,levels=paste0(c("ang","blip","blk","bump","cor","dop","sp"),".1.v4"))
levels(res.1.v4$scenario)=PLOTNAMES
ggplot(res.1.v4,aes(x=method,y=mise,fill=method)) + geom_violin() + facet_grid(.~scenario) + theme(axis.text.x=element_blank())
```

## Question

- Does anyone have applications where allowing for heteroskedastic errors might be useful?

## Summary

- We're looking for conspirators interested in organizing benchmarking!

## Thanks

- Zhengrong Xing

- to the developers of **R**, **knitr**, **Rstudio** and **Pandoc**.
Also the very cool **SQUAREM** and **wavethresh** packages.

- to the several postdoctoral researchers and students
who have worked with me on related topics.

- Including Chaoxing Dai, Mengyin Lu, Ester Pantaleo, Scott Powers, Sen Tian, Wei Wang, .

- NHGRI, Moore Foundation for funding.

- `ashr` package: `http://www.github.com/stephens999/ashr`

- `dscr` package: `http://www.github.com/stephens999/dscr`

>>>>

---
title: "Wavelet Vignette"
author: Matthew Stephens
date: May 22, 2015
output: ioslides_presentation
---

## Example: The "Blocks"" Function

@@

## Shrink + Backtransform = Smooth
```{r, echo=FALSE}
y.wd.thresh = wavethresh::threshold(y.wd, policy="BayesThresh")
y.est = wavethresh::wr(y.wd.thresh)
plot(x,mu,type="l",col=2,lwd=2)
lines(x,y.est,type="l")
```
